Investigating the applications and limits of single particle light scattering using limited detection schemes

### 2023-02-24 Latex files/Manuscript.tex
Tidying up repo

Our goal is to estimate the dimer orientation $\bar{\bf s}$ over time,
based on the scattering measurements $I(\bar{\bf s},\ \theta_k)$: the
question then is what set of angles ($\theta_1$, $\theta_2$,
$\theta_3$) give us the most useful information on $\hat{\bf s}$.  To
initially simplify the problem, rather than trying to get an exact
estimation of $\hat{\bf s}$, we discretise the orientation into
$n_{\rm ref}=30$ possible reference orientations $\hat{\bf n}_\alpha$
that are evenly distributed on the unit sphere \cite{Rey2006}.
%
We then consider how to optimise an experiment to identify the
reference orientation $\hat{\bf n}_\alpha$ that is closest to the
actual orientation $\hat{\bf s}$ of the dimer.
%
The method can be extended to an arbitrarily large number of reference
orientations, but for clarity and practicability we use a relatively
small number here; additionally, the choice of a small number of
discrete reference or ``candidate'' orientations also accounts for the
fact that any experiment will necessarily have a limited precision.
%
Using MSTM we compute the scattering that would be produced by the
dimer in each of the reference orientations, denoted as
$I(\hat{\bf n}_\alpha, \theta)$ and obtain ``measurements''
$I(\hat{\bf n}_\alpha, \theta_k)$ at our chosen set of angles
($\theta_1$, $\theta_2$, $\theta_3$).
%
These raw intensities are normalised according to
\begin{align}
\label{eq:scale}
  y_k(\hat{\bf n}_\alpha)
  = 
  \frac{I(\hat{\bf n}_\alpha, \theta_k) - \langle I(\hat{\bf n},\theta_k) \rangle } 
  {\langle I^2(\hat{\bf n},\theta_k) \rangle -\langle I(\hat{\bf n}, \theta_k)\rangle^2}
\end{align}
where the denominator is simply the standard deviation for our values
of $I(\hat{\bf n}, \theta_k)$.  The dimer's \emph{actual}
instantaneous scattered intensity, based on the real instantaneous
orientation $\bar{\bf s}$, is similarly scaled using
Eq.~\eqref{eq:scale} to give $y_1(\bar{\bf s})$, $y_2(\bar{\bf s})$,
and $y_k(\bar{\bf s})$.
%
The reference orientations, raw intensities, and scaled signals are
given in Tables~\ref{tab:A1} and \ref{tab:A2}.
%
In practice, $y_k(\bar{\bf s})$ will have an inherent amount of
uncertainty in our measurement due to noise from our detector.  We
compare our instantaneous signal to our reference signal by assuming
that the measurement uncertainty for each detection fibre is Gaussian
and is centred about $y_k(\bar{\bf s})$.
%
Combining all three detection angles provides us with the conditional
probability that, should the dimer be in orientation
$\hat{\bf n}_\alpha$, it would produce a signal ($y_1$, $y_2$, $y_3$):
\begin{align}
\label{eq:conditional}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  = \prod^3_{k=1}
(2\pi\sigma_k^2)^{-1/2} 
e^{-(y_{k}-y_{k}(\hat{\bf n}_\alpha))^2/2\sigma_k^2}
\end{align}
where $\sigma_k$ is related to the uncertainty in the detected signal
from our dimer $y_k(\bar{\bf s})$.  We left this as a tuneable
parameter to characterize the influence of experimental error on our
predictive method.  The signal error was simulated in our model by
stochastically adjusting our values of $y_k(\bar{\bf s})$.
\begin{eqnarray*}
  \sigma_k
  &= \epsilon\bar{y}(\hat{\bf n}_k)
  \\
  \Rightarrow y(\bar{\bf s}_k) &= y(\bar{\bf s})_k \pm n\sigma_k
  \\ 
n \in \mathbb{R}, n\in[0,1]
\end{eqnarray*} 
where $\epsilon$ is the percent error expected from our detection
fibres.  Equation~\eqref{eq:conditional} assigns a probability to each
reference orientation based on how similar the ``reference orientation
signal'' $y_{k}(\hat{\bf n}_\alpha)$ is to the actual signal
$y_{k}(\bar{\bf s})$ generated by the dimer in its real orientation
$\bar{\bf s}$.  However, if our values of $y_k(\hat{\bf n}_\alpha)$
are similar to one another, the probability distribution from
Eq.~\eqref{eq:conditional} will therefore assign similar probability
for multiple reference orientations.  Bayesian inference allows one to
update a probability distribution by accounting for information known
prior to making a measurement.  We apply this by accounting for our
distribution of reference orientations and instantaneous signals.
\begin{align}
  \label{eq:bayes}
  p(\hat{\bf n}_\alpha| y_1,y_2,y_3)
  &=
    \frac{p(y_1,y_2,y_3|\hat{\bf n}_\alpha)
    p(\hat{\bf n}_\alpha)}{p(y_1, y_2, y_3)}
\end{align}
where $p(\hat{\bf n}_\alpha)$ and $p(y_1, y_2, y_3)$ are the prior
estimates of the distributions of particle orientations and
instantaneous signals, respectively.  The former can be estimated by
some Boltzmann distribution based on how far apart reference
orientations are in physical space, covered in Section~\ref{sec:2.3}.
The latter prior $p(y)$ is the probability of our dimer producing a
signal $y_k(\bar{\bf s})$ that falls with our distribution of
reference signals $y_k(\hat{\bf n})$.  This is given by taking the
discrete integral over collection of reference orientations.
\begin{align}
  p(y_1, y_2, y_3)
  =
  \sum_{\alpha=1}^{n_{\rm ref}}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  p(\hat{\bf n}_\alpha)
\end{align}
The implementation of Eq.~\eqref{eq:bayes} improves our estimate by
suppressing reference orientations that are far away from our dimer's
orientation vector in physical space.  In order to evaluate the
accuracy of our method, we tested it using a Brownian dynamics
simulation of the dimer (see Section~\ref{sec:2.1}).

>>>>

Our goal is to estimate the dimer orientation $\bar{\bf s}$ over time,
based on the scattering measurements $I(\bar{\bf s},\ \theta_k)$: the
question then is what set of angles ($\theta_1$, $\theta_2$,
$\theta_3$) give us the most useful information on $\hat{\bf s}$.  To
initially simplify the problem, rather than trying to get an exact
estimation of $\hat{\bf s}$, we discretise the orientation into
$n_{\rm ref}=30$ possible reference orientations $\hat{\bf n}_\alpha$
that are evenly distributed on the unit sphere \cite{Rey2006}.
%
We then consider how to optimise an experiment to identify the
reference orientation $\hat{\bf n}_\alpha$ that is closest to the
actual orientation $\hat{\bf s}$ of the dimer.
%
The method can be extended to an arbitrarily large number of reference
orientations, but for clarity and practicability we use a relatively
small number here; additionally, the choice of a small number of
discrete reference or ``candidate'' orientations also accounts for the
fact that any experiment will necessarily have a limited precision.
%
Using MSTM we compute the scattering that would be produced by the
dimer in each of the reference orientations, denoted as
$I(\hat{\bf n}_\alpha, \theta)$ and obtain ``measurements''
$I(\hat{\bf n}_\alpha, \theta_k)$ at our chosen set of angles
($\theta_1$, $\theta_2$, $\theta_3$).
%
These raw intensities are normalised according to
\begin{align}
\label{eq:scale}
  y_k(\hat{\bf n}_\alpha)
  = 
  \frac{I(\hat{\bf n}_\alpha, \theta_k) - \langle I(\hat{\bf n},\theta_k) \rangle } 
  {\langle I^2(\hat{\bf n},\theta_k) \rangle -\langle I(\hat{\bf n}, \theta_k)\rangle^2}
\end{align}
where the denominator is simply the standard deviation for our values
of $I(\hat{\bf n}, \theta_k)$.  The dimer's \emph{actual}
instantaneous scattered intensity, based on the real instantaneous
orientation $\bar{\bf s}$, is similarly scaled using
Eq.~\eqref{eq:scale} to give $y_1(\bar{\bf s})$, $y_2(\bar{\bf s})$,
and $y_k(\bar{\bf s})$.
%
The reference orientations, raw intensities, and scaled signals are
given in Tables~\ref{tab:A1} and \ref{tab:A2}.
%
In practice, $y_k(\bar{\bf s})$ will have an inherent amount of
uncertainty in our measurement due to noise from our detector.  We
compare our instantaneous signal to our reference signal by assuming
that the measurement uncertainty for each detection fibre is Gaussian
and is centred about $y_k(\bar{\bf s})$.
%
Combining all three detection angles provides us with the conditional
probability that, should the dimer be in orientation
$\hat{\bf n}_\alpha$, it would produce a signal ($y_1$, $y_2$, $y_3$):
\begin{align}
\label{eq:conditional}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  = \prod^3_{k=1}
(2\pi\sigma_k^2)^{-1/2} 
e^{-(y_{k}-y_{k}(\hat{\bf n}_\alpha))^2/2\sigma_k^2}
\end{align}
where $\sigma_k$ is related to the uncertainty in the detected signal
from our dimer $y_k(\bar{\bf s})$.  We left this as a tuneable
parameter to characterize the influence of experimental error on our
predictive method.  The signal error was simulated in our model by
stochastically adjusting our values of $y_k(\bar{\bf s})$.
\begin{eqnarray*}
  \sigma_k
  &= \epsilon\bar{y}(\hat{\bf n}_k)
  \\
  \Rightarrow y(\bar{\bf s}_k) &= y(\bar{\bf s})_k \pm n\sigma_k
  \\ 
n \in \mathbb{R}, n\in[0,1]
\end{eqnarray*} 
where $\epsilon$ is the percent error expected from our detection
fibres.

Equation~\eqref{eq:conditional} gives the probability that a signal
($y_1$, $y_2$, $y_3$) will be measured if a dimer is in reference
orientation $\hat{\rm n}_\alpha$.
%
Using Bayes' theorem, the probability that the dimer is in reference
orientation $\hat{\bf n}_\alpha$, given that the signal ($y_1$, $y_2$,
$y_3$) is measured, can be estimated:
%
%
%
%update a probability distribution by accounting for information known
%prior to making a measurement.  We apply this by accounting for our
%distribution of reference orientations and instantaneous signals.
\begin{align}
  \label{eq:bayes}
  p(\hat{\bf n}_\alpha| y_1,y_2,y_3)
  &=
    \frac{p(y_1,y_2,y_3|\hat{\bf n}_\alpha)
    p(\hat{\bf n}_\alpha)}{p(y_1, y_2, y_3)}
\end{align}
where $p(\hat{\bf n}_\alpha)$ and $p(y_1, y_2, y_3)$ are the prior
estimates of the distributions of particle orientations and
instantaneous signals, respectively.
%
The former can be estimated by some Boltzmann distribution based on
how far apart reference orientations are in physical space, covered in
Section~\ref{sec:2.3}.  The latter prior $p(y)$ is the probability of
measuring a signal ($y_1$, $y_2$, $y_3$).  This is given by taking the
discrete integral over collection of reference orientations.
\begin{align}
  p(y_1, y_2, y_3)
  =
  \sum_{\alpha=1}^{n_{\rm ref}}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  p(\hat{\bf n}_\alpha)
\end{align}
The implementation of Eq.~\eqref{eq:bayes} improves our estimate by
suppressing reference orientations that are far away from our dimer's
orientation vector in physical space.  In order to evaluate the
accuracy of our method, we tested it using a Brownian dynamics
simulation of the dimer (see Section~\ref{sec:2.1}).
%
% based on how similar the ``reference orientation
%signal'' $y_{k}(\hat{\bf n}_\alpha)$ is to the actual signal
%$y_{k}(\bar{\bf s})$ generated by the dimer in its real orientation
%$\bar{\bf s}$.
%
However, if our values of $y_k(\hat{\bf n}_\alpha)$
are similar to one another, the probability distribution from
Eq.~\eqref{eq:conditional} will therefore assign similar probability
for multiple reference orientations.

### 2023-02-24 Latex files/Manuscript_rev2.tex
Tidying up repo

\begin{highlights}
\item Asymmetric dimers undergo a full inversion in the presence of an potential well. This only occurs if the size ratio is greater than 1:2.  
\item Orientations are classified by a combination of neural networks and Bayesian inference. 
\item Signal error has a significant effect on the performance of the neural network, this can be countered via biasing of the priori distribution. 
\item Future applications in continuos processes where particle size is changing with time are being considered.  
\end{highlights}

@@

Since the invention of optical tweezers in the late 1980's, they have
found applications in experiments ranging from single molecule
biophysics \cite{Bustamante2021Biophysics} to those that test the
fundamental assumptions of quantum mechanics \cite{yin2013large}
thanks mainly to the ability of the tweezer to transduce and detect
forces on the order of a few piconewtons. \textit{Further
  characterisation of the trapped entity would provide useful
  information, as explored in for example} metrological measurements
\cite{arita2020coherent} and colloidal aggregation
\cite{burns1990optical}. Chemical characterisation of the trapped
entities has been achieved using spectroscopic techniques such as
Raman Scattering \cite{gupta2014raman}, while dynamical
characterisation has been demonstrated using a Quadrant Photo
Detector, by following the centre-of-mass Brownian motion of the
trapped entity \cite{friedrich2012tuning} and measuring rotation of
the centre-of-mass \cite{yifat2021facile}.

@@

\subsection{Brownian Dynamics Simulation}
\label{sec:brownian}

Brownian dynamics simulations of the motion of a silica dimer trapped
in a highly focused Gaussian beam were performed using software
package Brownian~OT, developed by Fung~\textit{et~al}.\
\cite{Vigilante2020Brownian_OT} to simulate the motion of a asymmetric
dimer within an optical trap.  Brownian~OT combines MSTM
\cite{Mishchenko1996MSTM} and ``Optical Tweezer Toolbox''
(\textit{ott}) \cite{Lenton2020} to determine the optical forces and
torques on arbitrary clusters of spheres using the T-Matrix method.
%MSTM
%computes the T-matrix of the dimer, and then passes the T-matrix to
%\textit{ott} to compute the optical forces.
%The benefit of this approach is that MSTM can accurately compute the
%T-matrix for any arbitrary collection of spheres once, and then
%\textit{ott} can calculate the optical forces and torques.
%
The diffusion tensor of the dimer taken from Ref.~\citenum{Nir_Acrivos_1973}.
%Ref.~\citenum{Farsund1996}.
%
%The total displacement is the sum of the optical and Brownian
%contributions.
%
Brownian OT returns the dimer's motion as a \textit{csv} file
containing for each time step the $[x,y,z]$ position of the dimer's
centre of mass relative to the trap focus, and the orientation
represented as a quaternion.

@@

Our goal is to determine the orientation of our trapper dimer based on
the scattering measurements $I(\hat{n}, \theta_k)$ collected from
three detection fibres situated at $\theta_1$, $\theta_2$, $\theta_3$,
and $\theta_4$.  The dimer's orientation is discretized into
$n_{ref}=30$ reference orientations $\hat{\bf n}_{\alpha}$ that are
evenly distributed on a unit sphere \cite{Rey2006} (see
Figure~\ref{fig:dimer}~b).  The spacing between two neighbouring
reference orientations is roughly $0.895$~radians.

Using MSTM, we compute the raw intensities that would be collected
from the dimer in each reference orientation
$I(\hat{\bf n}_{\alpha}, \theta_k)$. We noticed that keeping all four
angles in the same plane resulted in identical signals, to counter
this we projected $\theta_4$ out of the horizontal plane and into the
vertical plane ($\phi = 90$) resulting in unique signals for each
reference orientation.
%
These raw intensities are normalized according to
\begin{align}
\label{eq:scale}
  y_k(\hat{\bf n}_\alpha)
  = 
  \frac{I(\hat{\bf n}_\alpha, \theta_k) - \langle I(\hat{\bf n},\theta_k) \rangle } 
  {\langle I^2(\hat{\bf n},\theta_k) \rangle -\langle I(\hat{\bf n}, \theta_k)\rangle^2}
\end{align}
where the denominator is simply the standard deviation for our values
of $I(\hat{\bf n}, \theta_k)$.  The reference orientations, raw
intensities, and scaled signals are given in Tables~\ref{tab:A1} and
\ref{tab:A2}.  The distribution of collected signals bares no specific
relationship with its associated reference orientation, this is an
inherent problem of the inverse light scattering pattern.

%Fortunately, for cases where the uncertainty in our signal
%measurements is low, we can easily predict the orientation by
%utilising computational techniques such as neural networks.

The inverse mapping from the scaled measured signal to a particular
reference orientation of the dimer was fit using a multi-layer
perceptron neural network with four hidden layers, each with 100
neurons logistic activation function.  This was implemented in Python
using the scikit-learn \cite{Pedregosa_etal_2011} library.
%to build a neural network for
%identifying the dimer's orientation from its light scattering
%signal.
The neural network was trained using the stochastic optimizer Adam
\cite{Kingma_Ba_014} on a data set that was generated by randomly
choosing $10^4$ orientations and calculating the corresponding scaled
signals from light scattering.
%
%
%and then having the network estimate the probability of the
%signal coming from our dimer in that corresponding reference
%orientation.  After making its estimation the network's loss function
%was evaluated and used to improve the estimation, we trained the
%network until the improvement in the loss function was less than
%$10^{-4}$.

The estimate provided by the neural network can be improved further by
accounting for any prior information we know about the dimer. We
therefore, utilise Bayesian inference to update our neural networks
estimation.
\begin{align}
  \label{eq:bayes}
  p(\hat{\bf n}_\alpha| y_k(\hat{\bf s}))
  &=
    \frac{p(y_k(\hat{\bf s})|\hat{\bf n}_\alpha)
    p(\hat{\bf n}_\alpha)}{p(y_k(\hat{\bf s}))}
\end{align}
where $p(\hat{\bf n}_\alpha)$ and $p(y_1, y_2, y_3)$ are the prior estimates of the distributions of particle orientations and instantaneous signals, respectively.
%
Without any prior evidence we assume that the orientation priori of our dimer
$p(\hat{\bf n}_{\alpha})$ is uniform. Knowledge of the dimer from previous
measurement can be used to inform our estimate of $p(\hat{\bf n}_{\alpha})$, covered in Section~\ref{sec:test}.  The latter prior $p(y)$ is the probability of measuring a signal ($y_1$, $y_2$, $y_3$).  This is given by taking the discrete integral over collection of reference orientations.
\begin{align}
  p(y_1, y_2, y_3)
  =
  \sum_{\alpha=1}^{n_{\rm ref}}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  p(\hat{\bf n}_\alpha)
\end{align}
From \eqref{eq:bayes} we get a mass probability distribution that denotes the
probability that our dimer is in orientation $\hat{\bf n}_{\alpha}$ given a
signal ($y_1$, $y_2$, $y_3$). In order to evaluate the accuracy of our method, we tested it using a Brownian dynamics simulation of the dimer (see Section~\ref{sec:brownian}).

>>>>

\begin{highlights}
\item Asymmetric dimers undergo a full inversion in the presence of an potential well. This only occurs if the size ratio is greater than 1:2.  
\item Orientation can be classified by applying Bayesian inference to light intensity signals. 
\item The choice of detection angles has no noticeable effect on the performance of characterising orientation.
\item Performance of model is determined in part due to uncertainty in the measurement precision. 
\item Future applications in continuos processes where particle size is changing with time are being considered.  
\end{highlights}

@@

Since their invention in the late 1980's, Optical Tweezers have found application in experiments ranging from single molecule biophysics \cite{Bustamante2021Biophysics} to those that test the fundamental assumptions of Quantum Mechanics  \cite{yin2013large} thanks mainly to the ability of the tweezer to transduce and detect forces on the order of a few pico newtons. \textit{Further characterisation of the trapped entity would provide useful information, as explored in for example} metrological measurements \cite{arita2020coherent} and colloidal aggregation \cite{burns1990optical}. Chemical characterisation of the trapped entities has been achieved using spectroscopic techniques such as Raman Scattering \cite{gupta2014raman}, while dynamical characterisation has been demonstrated using a Quadrant Photo Detector,  by following the centre-of-mass Brownian motion of the trapped entity  \cite{friedrich2012tuning} and measuring rotation  of the centre-of-mass \cite{yifat2021facile}.

@@

\subsection{Brownian Simulation}
\label{sec:brownian}

We use the Brownian OT package developed by Fung~\textit{et~al}. \cite{Vigilante2020Brownian_OT} to simulate the motion of a asymmetric dimer within an optical trap. Brownian OT combines MSTM \cite{Mishchenko1996MSTM} and ``Optical Tweezer Toolbox'' (\textit{ott}) \cite{Lenton2020} to simulate the motion of arbitrary
shaped sphere clusters. We simulated the motion of a silica dimer
trapped in a highly focused Gaussian beam.

The dimer's Brownian motion is simulated by calculating its diffusion tensor according to Farsund's \emph{et al} work \cite{Farsund1996}. For computing the optical force Brownian OT uses the T-Matrix method to calculate scattering of the dimer. MSTM computes the T-matrix of the dimer, and then passes the T-matrix to \textit{ott} to compute the optical forces. The benefit of this approach is that MSTM can accurately compute the T-matrix for any arbitrary collection of spheres once, and then \textit{ott} can calculate the optical forces and torques. The total displacement is the sum of the optical and Brownian contributions.

Brownian OT returns the dimer's motion as a \textit{csv} file containing for each time step the $[x,y,z]$ position of the dimer's centre of mass relative to the trap focus, and the orientation represented as a quaternion.

@@

Our goal is to determine the orientation of our trapper dimer based on the scattering measurements $I(\hat{n}, \ \theta_k)$ collected from three detection fibres situated at $\theta_1,\ \theta_2, \ \theta3, \ \& \ \theta_4$. Rather than get an exact estimate of the dimer's orientation the possible orientation space is discretized into $\textit{n}_{ref} \ = \ 30$ possible reference orientations $\hat{\bf n}_{\alpha}$ that are evenly distributed on a unit sphere \cite{Rey2006}, see Figure~\ref{fig:dimer} b. The maximum spacing between two neighbouring reference orientations is roughly 0.895 radians.

Using MSTM we compute the raw intensities that would be collected from the dimer in each reference orientation $I(\hat{\bf n}_{\alpha}, \theta_k)$. We noticed that keeping all four angles in the same plane resulted in identical signals, to counter this we projected $\theta_4$ out of the horizontal plane and into the vertical plane ($\phi = 90$) resulting in unique signals for each reference orientation. 
%
These raw intensities are normalized according to
\begin{align}
\label{eq:scale}
  y_k(\hat{\bf n}_\alpha)
  = 
  \frac{I(\hat{\bf n}_\alpha, \theta_k) - \langle I(\hat{\bf n},\theta_k) \rangle } 
  {\langle I^2(\hat{\bf n},\theta_k) \rangle -\langle I(\hat{\bf n}, \theta_k)\rangle^2}
\end{align}
where the denominator is simply the standard deviation for our values of $I(\hat{\bf n}, \theta_k)$. The reference orientations, raw intensities, and scaled signals are given in Tables~\ref{tab:A1} and \ref{tab:A2}. The distribution of collected signals bares no specific relationship with its associated reference orientation, this is an inherent problem of the inverse light scattering pattern. Fortunately, for cases where the uncertainty in our signal measurements is low, we can easily predict the orientation by utilising computational techniques such as neural networks.

We utilised a python machine learning program called scikit-learn to build a neural network for identifying the dimer's orientation from its light scattering signal. The network was trained by generating a database of random orientation vectors, calculating the light scattering signals, and then having the network estimate the probability of the signal coming from our dimer in that corresponding reference orientation. After making its estimation the network's loss function was evaluated and used to improve the estimation, we trained the network until the improvement in the loss function was less than 0.0001. 
%
The estimation provided by the neural network can be improved further by accounting for any prior information we know about the dimer. We therefore, utilise Bayesian inference to update our neural networks estimation.

\begin{align}
  \label{eq:bayes}
  p(\hat{\bf n}_\alpha| y_k(\hat{\bf s}))
  &=
    \frac{p(y_k(\hat{\bf s})|\hat{\bf n}_\alpha)
    p(\hat{\bf n}_\alpha)}{p(y_k(\hat{\bf s}))}
\end{align}
where $p(\hat{\bf n}_\alpha)$ and $p(y_1, y_2, y_3)$ are the prior estimates of the distributions of particle orientations and instantaneous signals, respectively.
%
Without any prior evidence we assume that the orientation priori of our dimer
$p(\hat{\bf n}_{\alpha})$ is uniform. Knowledge of the dimer from previous
measurement can be used to inform our estimate of $p(\hat{\bf n}_{\alpha})$, covered in Section~\ref{sec:test}.  The latter prior $p(y)$ is the probability of measuring a signal ($y_1$, $y_2$, $y_3$).  This is given by taking the discrete integral over collection of reference orientations.
\begin{align}
  p(y_1, y_2, y_3)
  =
  \sum_{\alpha=1}^{n_{\rm ref}}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  p(\hat{\bf n}_\alpha)
\end{align}
From \eqref{eq:bayes} we get a mass probability distribution that denotes the
probability that our dimer is in orientation $\hat{\bf n}_{\alpha}$ given a
signal ($y_1$, $y_2$, $y_3$). In order to evaluate the accuracy of our method, we tested it using a Brownian dynamics simulation of the dimer (see Section~\ref{sec:brownian}).

### 2023-02-24 Latex files/Optimizationnotes.tex
Tidying up repo

The experiemental set up that this is based on is a inverted microscope optical trap, a suspension of microparticles are loaded onto a plastic cover slide. Onto the slide four optical fibres are stuck down; one fibre walks a 633 nm HeNe laser onto the cover slip pointed directly at the trap focus, and the 3 remaining fibres are spaced equidistantly from the trap focus. The distance between each fibre and the trap focus is roughly $200\mu m$, with the exact angles between the particle and the trap focus being measured via the microcopes camera. The trapping laser is a 1064 nm NIR laser that is introduced via a 1.25 NA objective; to increase the trapping depth of the objective a lense of focal length 100 cm was added into the beam path to transform the profile entering the objective from parallel to converging, as advised by []'s paper.

@@

\subsection*{Further improvements}
While our model provides a satisfactory prediction of the dimer's motion; ideally this model can be exteneded to any particle characteristic that has a clear effect on the scattering from the trapped entity. For example using the mstm package we can determine how differently sized particles in similar orientations will produce different scattering patterns.

>>>>

We are currently developing an experimental set up that will allow us to light scattering

@@
